---
title: "assignment4"
author: "Xi Cheng"
date: "February 21, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##10.5.1
```{r,echo=FALSE}
library(tidyverse)


```

```{r}
is.tibble(mtcars)
```
So, if we can open the data.frame with tibble, then it's a tibble data.frame. If we have to open it with as_tibble(), then it is a regular data.frame. And also, we can use is.tibble() to find out if it is a tibble or just a normal data.frame.

##10.5.2
```{r, echo=FALSE}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```
if we want to subset some data from regular data.frame, we have to consider about the rows and columns. However, if we use tibble, we could just consider the columns.
##10.5.3

var <- "mpg"
var[["mpg"]]
var %>% .$mpg
var %>% .[["mpg"]]


##10.5.4

```{r,echo=FALSE}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
annoying
```
###10.5.4.1
```{r,echo=FALSE}
annoying$`1`
```
###10.5.4.2
```{r,echo=FALSE}
ggplot(annoying,aes(x=`1`,y=`2`))+geom_point()

```

##10.5.4.3
```{r,echo=FALSE}
add_column(annoying, '3' = annoying$`2`/annoying$`1`)
annoying[["3"]] <- annoying[["2"]] / annoying[["1"]]
annoying
```
##10.5.4.4
```{r,echo=F}
annoying <- rename(annoying, one = `1`, two = `2`, three = `3`)
annoying

```
##10.5.5
enframe() converts named atomic vectors or lists to two-column data frames. For unnamed vectors, the natural sequence is used as name column.

##10.5.6
print.tbl_df

#########################################
#########################################

#12.6.1
```{r,echo=FALSE}
who
who1 <- who %>% 
  gather(new_sp_m014:newrel_f65, key = "key", value = "cases", na.rm = TRUE)
who1 %>% 
  count(key)
who2 <- who1 %>% 
  mutate(key = stringr::str_replace(key, "newrel", "new_rel"))
who3 <- who2 %>% 
  separate(key, c("new", "type", "sexage"), sep = "_")
who3 %>% 
  count(new)
who4 <- who3 %>% 
  select(-new, -iso2, -iso3)
who5 <- who4 %>% 
  separate(sexage, c("sex", "age"), sep = 1)
who5

```

we use na.rm = T in this case is reasonable, because there are lots of NA values in the data which is useless. we can use count(cases=NA) find out the all these missing values.


```{r}
count(who,cases = NA)

```

##12.6.2
The code will not be separated properly into the three columns new, var, and sexage.

##12.6.3
```{r,echo= F}
select(who3, country, iso2, iso3) %>% distinct() %>% group_by(country) %>% filter(n() > 1)
```

##12.6.4

```{r,echo=FALSE}
who5 %>%
  group_by(country, year, sex) %>%
  filter(year > 1995) %>%
  summarise(cases = sum(cases)) %>%
  unite(country_sex, country, sex, remove = FALSE) %>%
  ggplot(aes(x = year, y = cases, group = country_sex, colour = sex)) +
  geom_line()




```











